Outputs from time slice analyses

### 2017-12-05 analyses/04-stats.Rmd
extinction csv saved

## Significant results
result <- cbind(results, apply(result[,7:9], 2, function(col) ifelse(col < 0.05, TRUE, FALSE)))

## Print the table
knitr::kable(result)
```

>>>>

## Significant results
result <- cbind(result, apply(result[,7:9], 2, function(col) ifelse(col < 0.05, TRUE, FALSE)))

## Print the table
knitr::kable(result)

## Save the results
write.csv(result, file = paste0("../outputs/extinction.", slug, ".csv"), quote = FALSE, 
          row.names = FALSE)

```
